\LARGE \bf Longitudinal Trajectory Planning and Tracking for Fixed-Path Autonomous Driving

### 2016-01-19 paper1.tex
redid notation in 7phase graphic, and made it bigger
removed Ambarish as author

\author{
  Robert G. Cofield $^{1}$,
  Rakesh Gupta $^{2}$,
  Ambarish Goswami $^{3}$,
  and
  David Bevly $^{4}$
  \thanks{
    * This work was performed at Honda Research Institute USA.
  }
  \thanks{
    $^{1}$ Auburn University, Dept. of Mechanical Engineering, GPS \& Vehicle Dynamics Laboratory.
  }
  \thanks{
    $^{2}$ Honda Research Institute USA
  }
  \thanks{
    $^{3}$ Honda Research Institute USA
  }
  \thanks{
    $^{4}$ Auburn University, Dept. of Mechanical Engineering, GPS \& Vehicle Dynamics Laboratory.
  }
}

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=1.0\columnwidth]{graphics/Full7PhaseSpecVertical.png}
  \caption{7 phase constant jerk profile along curvilinear distance axis.}
  \label{fig:full7phasespec}
\end{figure}

>>>>

\author{
  Robert G. Cofield $^{1}$,
  Rakesh Gupta $^{2}$,
  and
  David Bevly $^{4}$
  \thanks{
    * This work was performed at Honda Research Institute USA.
  }
  \thanks{
    $^{1}$ Auburn University, Dept. of Mechanical Engineering, GPS \& Vehicle Dynamics Laboratory.
  }
  \thanks{
    $^{3}$ Honda Research Institute USA
  }
  \thanks{
    $^{4}$ Auburn University, Dept. of Mechanical Engineering, GPS \& Vehicle Dynamics Laboratory.
  }
}

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=1.0\columnwidth]{graphics/Full7PhaseSpecVertical.png}
  \caption{7 phase constant jerk profile along curvilinear distance axis. All values needed to completely parameterize a single path segment for trajectory are labelled here.}
  \label{fig:full7phasespec}
\end{figure}
